---
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
library(dplyr)
library(sf)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
#knitr::read_chunk("data-raw/download_2016.R")
```

# Overview

The goal of comorosmpas is to get maps of Comoro Islands to plot!

# Installation

Install from CRAN with 

```{r install, eval=FALSE}
install.packages("comorosmaps")
```

The development version of comorosmaps may be installed directly from github. 

```{r dev-install, eval = FALSE}
devtools::install_github("hhousni/comorosmaps")
```

## Usage

Plot Comoro islands as one country without region. 

```{r }
library(comorosmaps)
comoros()
```

Plot Comoro islands as one country with region. 

```{r }
comoros(pref = TRUE)
```

Plot Moheli island without region. 

```{r }
moheli()
```

Plot Moheli island with region. 

```{r }
moheli(pref = TRUE)
```

Plot Anjouan island without region. 

```{r }
anjouan()
```

Plot Moheli island with region. 

```{r }
anjouan(pref = TRUE)
```

Plot Grande Comore island without region. 

```{r }
grandeComore()
```

Plot Grande Comore island with region. 

```{r }
grandeComore(pref = TRUE)
```
